Competing Bandits: \\ The Perils of Exploration under Competition

### 2018-11-06 paper/content/inverted_u.tex
Minor edits.

\gaedit{
\xhdr{Welfare}

\swedit{We also study the effects the competition has on the consumer
  welfare---the cumulative rewards received by the users over time.}

@@

\swedit{For our purpose, it will be clearer to look at \emph{market
    regret}: the difference between the cumulative mean rewards
  achieved by taking the best action over all rounds and the
  cumulative mean rewards received by the agents. (Hence smaller
  regret means higher welfare.)}

@@

\swedit{We also observe that monopoly and duopoly achieve similar
  welfare, with monopoly being marginally better than duopoly. This is
  surprising since one might conjecture that the welfare should
  increase with the number of firms playing \DG since more $\DG$ runs
  should result in faster concentration on playing the better arms. In
  particular,, more firms playing \DG should result in faster
  discovery of a better arm, and the firm with such discovery would be
  able to attract more consumers and increase market welfare.}
\begin{figure}
\includegraphics[scale=0.3]{figures/eeog_vs_num_ht}
\includegraphics[scale=0.3]{figures/ht_many_firm_welfare}\\
\caption{Average welfare and EEOG as we increase \#firms playing \DG}
\label{many_firm_welfare}
\end{figure}

\swedit{To study this phenomenon further, we go beyond the two-firm
  setting and simulate the game an increasing number of firms playing
  \DG.} Figure \ref{many_firm_welfare} reports the average welfare
across these simulations. Welfare not only does not get better,
\textit{but is weakly worse} as we increase the number of
firms. Correspondingly, we track the average \Eeog in each of the
simulations and notice that it is \textit{increasing} as the number of
firms increases. As we increase the number of firms, a single
individual firm gets fewer consumers for learning as consumers switch
between firms more often. Additionally, bad luck with rewards or arm
selection is punished even more harshly as we increase the number of
firms. This further strengthens the intuition from our previous
result, which is that learning may be hard under competition since
exploration and mistakes are punished harshly but are necessary for
learning.}

>>>>

\xhdr{Welfare.}
We also study the effects of the competition on the consumer welfare---the total reward received by the users over time.

@@

\asedit{Rather than the welfare directly, we find it more illuminating to consider} \emph{market regret}: the difference between the cumulative mean rewards achieved by taking the best action over all rounds and the cumulative mean rewards received by the agents. (Hence smaller regret means higher welfare.)

@@

\swedit{We also observe that monopoly and duopoly achieve similar
  welfare, with monopoly being marginally better than duopoly. This is
  surprising since one might conjecture that the welfare should
  increase with the number of firms playing \DG since more $\DG$ runs
  should result in faster concentration on playing the better arms. In
  particular, more firms playing \DG should result in faster
  discovery of a better arm, and the firm with such discovery would be
  able to attract more consumers and increase market welfare.}
\begin{figure}
\includegraphics[scale=0.3]{figures/eeog_vs_num_ht}
\includegraphics[scale=0.3]{figures/ht_many_firm_welfare}\\
\caption{Average welfare and EEOG as we increase \#firms playing \DG}
\label{many_firm_welfare}
\end{figure}

\swedit{To study this phenomenon further, we go beyond the two-firm
  setting and simulate the game an increasing number of firms playing
  \DG.} Figure \ref{many_firm_welfare} reports the average welfare
across these simulations. Welfare not only does not get better,
\textit{but is weakly worse} as we increase the number of
firms. Correspondingly, we track the average \Eeog in each of the
simulations and notice that it is \textit{increasing} as the number of
firms increases. As we increase the number of firms, a single
individual firm gets fewer consumers for learning as consumers switch
between firms more often. Additionally, bad luck with rewards or arm
selection is punished even more harshly as we increase the number of
firms. This further strengthens the intuition from our previous
result, which is that learning may be hard under competition since
exploration and mistakes are punished harshly but are necessary for
learning.
